Incentivizing Exploration with Unbiased Histories

### 2019-04-16 2level.tex
Proofs in the warmup section: moved the short proof back to the body; the longer proof, made it the last subsection in the section.

\OMIT{ %%%%%%
\begin{proof}[Proof Sketch]
\ascomment{Jieming, pls add a brief proof sketch if you can.}
\jmcomment{The main idea of the proof is to consider the case when all pulled arms have bad realized rewards (i.e. 0). }
\jmcomment{Actually, not clear about how to write a sketch for a proof of 8 lines.}
\end{proof}
} %%%%%%

@@

The proofs can be found in Appendix~\ref{app:warmup}. One important quantity is the expected number of samples of a given arm $a$ collected by a full-disclosure path $S$ of length $\fdpL$ (\ie present in the subhistory $\SubH{S}$. Indeed, this number, denoted $\fdpN$, is the same for all such paths. Then,

@@

>>>>

\begin{proof}
  Fix any arm $a$. Let $\GdT = (K-1) \cdot \estN + 1$ and
  $\GdP = (1/3)^{\GdT}$. We will condition on the event that
    all the realized rewards in $\GdT$ rounds are 0, which occurs with
    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.
  In this case, we want to show that arm $a$ is pulled at least
  once. We prove this by contradiction. Suppose arm $a$ is not pulled. By
  the pigeonhole principle, we know that there is some other arm $a'$
  that is pulled at least $\estN + 1$ rounds. Let $t$ be the round in
  which arm $a'$ is pulled exactly $\estN + 1$ times. By Assumption
  \ref{ass:embehave}, we know
  \[
    \hat{\mu}_{a'}^t \leq 0 + \estC / \sqrt{\estN}  \leq \estC < 1/3.
  \]
  On the other hand, we have
  $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
  the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
\end{proof}

@@

The proof can be found in Section~\ref{app:warmup}. One important quantity is the expected number of samples of a given arm $a$ collected by a full-disclosure path $S$ of length $\fdpL$ (\ie present in the subhistory $\SubH{S}$. Indeed, this number, denoted $\fdpN$, is the same for all such paths. Then,

@@

\input{app-warmup}

### 2019-04-16 app-warmup.tex
Proofs in the warmup section: moved the short proof back to the body; the longer proof, made it the last subsection in the section.

%!TEX root = main.tex
\section{Proofs from Section~\ref{sec:warmup}}
\label{app:warmup}

\begin{proof}[Proof of Lemma~\ref{lem:greedy}]
  Fix any arm $a$. Let $\GdT = (K-1) \cdot \estN + 1$ and
  $\GdP = (1/3)^{\GdT}$. We will condition on the event that
    all the realized rewards in $\GdT$ rounds are 0, which occurs with
    probability at least $\GdP$ under Assumption~\ref{ass:embehave}.
  In this case, we want to show that arm $a$ is pulled at least
  once. We prove this by contradiction. Suppose arm $a$ is not pulled. By
  the pigeonhole principle, we know that there is some other arm $a'$
  that is pulled at least $\estN + 1$ rounds. Let $t$ be the round in
  which arm $a'$ is pulled exactly $\estN + 1$ times. By Assumption
  \ref{ass:embehave}, we know
  \[
    \hat{\mu}_{a'}^t \leq 0 + \estC / \sqrt{\estN}  \leq \estC < 1/3.
  \]
  %\nicomment{Wait, where did we set $\estN$?} 
  On the other hand, we have
  $\hat{\mu}_a^t \geq 1/3 > \hat{\mu}_{a'}^t$. This contradicts with
  the fact that in round $t$, arm $a'$ is pulled, instead of arm $a$.
  %\swdelete{ In addition, we know that this case happens with
    %probability at least $(1/3)^{\GdT} = \GdP$ as each arm's mean is
    %at most $2/3$. To sum up, we know that with probability at least
    %$\GdP$, \ALGG of $\GdT$ rounds pulls arm $a$ at least once.}
  % \jmcomment{Agree with these changes.}
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:2level}]
  We will set $T_1$ later in the proof, depending on whether the gap
  parameter $\Delta$ is known. For now, we just need to know we will
  make $T_1 \geq \frac{4(\GdT)^2}{(\GdP)^2}\log(T)$. Since this policy is
  agnostic to the indices of the arms, we assume w.l.o.g. that arm 1
  has the highest mean.

@@

For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
\[
|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}.
\]
By $W_1$ and Assumption \ref{ass:embehave}, we have
\[
|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{\estC}{\sqrt{\fdpN T_1/2}}.
\]
Therefore,
\[
|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}+\frac{\estC}{\sqrt{\fdpN T_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total regret is at most
\[
T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get regret $O(T^{2/3}\log(T)^{1/3})$.
\OMIT{Notice that if we know the gap parameter is known to be larger than
$\Delta$, we can set
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
This completes the proof.}
\end{proof}

>>>>

%!TEX root = main.tex
\subsection{Proof of Theorem~\ref{thm:2level}}
\label{app:warmup}

  We will set $T_1$ later in the proof, depending on whether the gap
  parameter $\Delta$ is known. For now, we just need to know we will
  make $T_1 \geq \frac{4(\GdT)^2}{(\GdP)^2}\log(T)$. Since this policy is
  agnostic to the indices of the arms, we assume w.l.o.g. that arm 1
  has the highest mean.

@@

For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
\[
|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}.
\]
By $W_1$ and Assumption \ref{ass:embehave}, we have
\[
|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{\estC}{\sqrt{\fdpN T_1/2}}.
\]
Therefore,
\[
|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{\fdpN T_1 /2}}+\frac{\estC}{\sqrt{\fdpN T_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total regret is at most
\[
T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get regret $O(T^{2/3}\log(T)^{1/3})$.
